\documentclass[letterpaper,12pt,oneside]{article}

\usepackage{fullpage}
\usepackage{amssymb}

\newcommand{\Athena}[0]{$A \Theta \eta \nu \alpha$}

\begin{document}

\title{Impact of the transition to the reputation-confidence based market.}
\author{Alex Lee and William Nowak}

\maketitle

\section{Introduction}
The ``TBall'' game has been played with the concept of money (or even life
energy), much akin to the popular role-playing games. The transition to a
reputation-confidence based market impacts our agent -- Athena.

\section{The academic metaphor}

\subsection{Problems do not come from the students.}
Students do not ask the professor to solve a problem. Students do not ask
other students to solve a problem. The way, as it has been for centuries,
is that the professor asks, and the students try to answer -- especially
during an examination. How can we evaluate a student based on a problem
another student asks?

When the competition is linked to our grades, it is in our collective
interest to tie. However, it seems that the Nash equilibrium has won for
now (where the stronger teams prevented the weakers ones from receiving
an A). There is no barrier preventing the students to form a pact;
our agents will always re-offer, making the game uninteresting while we
collectively receive A's.

For the game to make sense, the requirement that the agents produce
problems has to be removed (or that they interact with each other). After
all, the ability to generate problems is not in question.

\subsubsection{The world without a market.}

The difficulty of an instance of a {\tt MAX-CSP} problem depends on three
factors:
\begin{itemize}
    \item The number of variables.
    \item The number of clauses.
    \item The type(s) of the clauses (relation numbers).
\end{itemize}

The solution to such problem is the assignment of variables where the
maximum number of clauses are satisfied. The benchmark to {\tt MAX-CSP}
is how fast you can arrive at the solution.

The sixty second limit per turn should be changed. The time limit should
linearly correspond to the number of questions one has to solve and the
number of questions one has to generate.

The user may want to know which agent (algorithm) is the fastest.
Currently, the administrator and the protocol both do not have the faculty
to provide such information (since all transactions are globbed together).

\subsubsection{Bringing back the classroom.}

Let us define ``reputation''. A reputation is the collective opinion
of an individual entity. This suggests that the reputations depend on a
human construct contingent on cognition -- our opinion. Using such logic
will harm the process in discovering the best agent, since our opinions
will be inherently human.

Suppose that we keep the old system in place where ``reputations''
are being transacted. The administrator governs why and where these
``reputations'' go.  The metaphor would not make any sense. It is wrong
to assign numeric value to reputation.

\section{The impact on Athena}

There is no doubt that when the administrator changes, all agents based
on the ``Baby Agent'' get a free upgrade that they really should not get.
Athena has a comparative disadvantage when the specification changes,
but there is enough discrepency in speed (C versus Java \texttrademark)
to make up for those changes.

\end{document}
